### 2016-09-30 GBF-private-M.tex

%\begin{theorem}\label{thm:gbf-correctness-privM}
%Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
%\[
%\AdvCorrect{\setprim_{\mathrm{garb}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
%\]
%\end{theorem}
\begin{proof}[Theorem~\ref{thm:gbf-correctness-privM}]
We use a game playing argument to prove this theorem. Here, $\Rep$, $\Qry$ and $A$ are given access to $\Hash$ which uses lazy sampling to mimic a RO. Game $\game{0}$ exactly simulates the correctness game of a private-$M$ garbled Bloom filter in the ROM. \tsnote{No, the hash oracle is different because it returns~$k$ values at once.}

Game~$\game{1}$ is equivalent to game~$\game{0}$ under the assumption that~$A$ does not make any pointless random-oracle queries, the $\Hash$ returns random values sampled from $[m]$ in $\game{1}$. In order to account for queries to RO in $\Test$, the latter returns the $k$ hash values for each query along with the answer. It should be noted that the $\Qry$ oracle returns xor of shares at $k$ random positions in this game. \tsnote{No, $\Qry$ just returns the answer~$a$.}

@@

\begin{figure}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{$\game{0}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
$h_1,\ldots,h_k \gets \HashOracle(\qry_x)$\\
Return~$a, h_1,\ldots,h_k $\\

\oracle{$\HashOracle(\qry_y)$}\\
$v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\HashOracle(\qry_y)$}\\
$v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\HashOracle(\qry_y)$}\\
$v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm:gbf-correctness-privM}: Game playing argument}\label{fig:GBFprivMGame}
\end{figure}

>>>>

%\begin{theorem}\label{thm:gbf-correctness-privM}
%Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
%\[
%\AdvCorrect{\setprim_{\mathrm{garb}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
%\]
%\end{theorem}
\begin{proof}[\Cref{thm:gbf-correctness-privM}]
We use a game playing argument to prove this theorem. Here, $\Rep$, $\Qry$ and $A$ are given access to $\Hash$ which uses lazy sampling to mimic a RO. $\game{0}$, exactly simulates the correctness game of a garbled Bloom filter for private $M$. Assuming $A$ does not make any pointless queries, the $\Hash$ returns random values sampled from $[m]$ in $\game{1}$. In order to account for queries to RO in $\Test$, the latter returns the $k$ hash values for each query along with the answer. It should be noted that the $\Qry$ oracle returns xor of shares at $k$ random positions in this game.

@@

\begin{figure}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$(h_1,\ldots,h_k \getsr [m]$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a, h_1,\ldots,h_k $\\

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

@@

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm:gbf-correctness-privM}: Game playing argument}\label{fig:GBFprivMGame}
\end{figure}
